A Graph-based Framework for Coverage Analysis in Autonomous Driving \newline \newline Preprint

### 2025-11-19 article/article.tex
start summary writing

\begin{itemize}
    \item We apply the subgraph isomorphism approach to both the  CARLA and the Argoverse data to identify coverage scenarios.
    \item The archetypes used here are defined manually and described in table xxx. The chosen archetypes are typical traffic situations like e.g. lead vehicle situations, lane change situations or different combinations of opposite direction vehicles.
    \item Also, information like which traffic actors are on an intersection are incorporated into the archetypes.
    \item The results are shown in Figure \ref{fig:subgraph_isomorphism_coverage_barcharts} to Figure \ref{fig:subgraph_isomorphism_agreement_matrix_manual_scenarios_carla}.
    \item In Figure \ref{fig:subgraph_isomorphism_coverage_barcharts} there is a clear signal that for both datasets the coverage is not uniform.
    \item Also, the distribution for the Carla dataset is not close to the Argoverse distribution, indicating that the CARLA data is not representative for the Argoverse data.
    \item Even worse, the Carla dataset is nearly completely missing out e.g. on the cut\_out\_intersection archetype, clearly indicating a coverage gap in the Carla dataset.
\end{itemize}

@@

\begin{table}[htbp]
    \caption{My Table}
    \label{tab:mytable}
    \begin{tabular}{rrrrr}
    \toprule
    scn 1 & scn 2 & scn 3 & scn 4 & size \\
    \midrule
    False & False & False & False & 613 \\
    False & False & True & False & 3 \\
    True & True & False & True & 377 \\
    True & True & True & True & 7 \\
    \bottomrule
    \end{tabular}
\end{table}
% \cite{goodfellow2016deep} % needed?

@@

The resulting embeddings have been analysed in a number of ways. For plausibility checks, for a number of 
randomly samples scenarios, the scenario with 
closest embedding vector (euclidean distance as well as cosine distance) has been visualized. 
This is shown in Figure \ref{fig:plausibility_checks}. This 
includes comparison between CARLA and Argoverse scenarios.

@@

The results for this approach are shown in Section xxx.

@@

>>>>

We apply the subgraph isomorphism approach to both the  CARLA and the Argoverse data to identify coverage scenarios.
The archetypes used here are defined manually and described in table xxx. The chosen archetypes are typical traffic situations like e.g. lead vehicle situations, lane change situations or different combinations of opposite direction vehicles.
Also, information like which traffic actors are on an intersection are incorporated into the archetypes.
The results are shown in Figure \ref{fig:subgraph_isomorphism_coverage_barcharts} to Figure \ref{fig:combined_distributions_plots_speed_distance_argo}.
In Figure \ref{fig:subgraph_isomorphism_coverage_barcharts} there is a clear signal that for both datasets the coverage is not uniform per the different archetypes.
Also, the distribution for the Carla dataset is not close to the Argoverse distribution, indicating that the CARLA data is not representative for the Argoverse data.
Even worse, the Carla dataset is nearly completely missing out e.g. on the cut\_out\_intersection archetype, clearly indicating a coverage gap in the Carla dataset.
A next step of analysis is to check, which archetypes are occuring simultaneously in a traffic scene. 
Figure \ref{fig:subgraph_isomorphism_agreement_matrix_manual_scenarios} shows the agreement matrix for the manually defined coverage scenarios for CARLA and Argoverse.
The heatmaps show the percentage of agreement between the manually defined coverage scenarios for CARLA and Argoverse.

TODO: Write a sentence about the agreement matrices once using the actual actor graph defintion.

A last example of how to use the assignment of archetypes to traffic scenes is to check the parameter distribution for the speed and path length of the traffic scenes.
Figure \ref{fig:combined_distributions_plots_speed_distance_carla} and Figure \ref{fig:combined_distributions_plots_speed_distance_argo} show the parameter distribution for the speed and path length of the traffic scenes for CARLA and Argoverse.
The plots show that the distribution for the CARLA data is not close to the Argoverse distribution, indicating that the CARLA data is not representative for the Argoverse data.
Given the assignment of archetypes to traffic scenes based on the actors can be used in further analysis not done here, e.g. to check more divers parameters and distributions.

@@

% \begin{table}[htbp]
%     \caption{My Table}
%     \label{tab:mytable}
%     \begin{tabular}{rrrrr}
%     \toprule
%     scn 1 & scn 2 & scn 3 & scn 4 & size \\
%     \midrule
%     False & False & False & False & 613 \\
%     False & False & True & False & 3 \\
%     True & True & False & True & 377 \\
%     True & True & True & True & 7 \\
%     \bottomrule
%     \end{tabular}
% \end{table}
% % \cite{goodfellow2016deep} % needed?

@@

The resulting embeddings have been analysed in a number of ways. For plausibility checks, for a number of 
randomly samples scenarios, the scenario with 
closest embedding vector (euclidean distance) has been visualized. 
This is shown in Figure \ref{fig:plausibility_checks}. This 
includes comparison between CARLA and Argoverse scenarios.

@@

@@

\begin{itemize}
    \item A method for using traffic scenes represented as graphs for coverage analysis has been developed in this paper.
    \item Starting from defining rules for the actor graph construction, the resulting graphs are then used by 2 different approaches for coverage analysis.
    \item Firstly, a non-AI approach is used where a set of archetypes is defined (which is done here manually but in principle could be done automatically as well).
    \item Then it is checked, which archetypes are present in a traffic scene and how often.
    \item Secondly, a graph embedding approach is used to create a vector space of the traffic scenes and to check if the target distribution is met by the test distribution in the embedded space.
    \item The results for this approach are shown in Section \ref{chapter:application}, being applied to Carla and Argoverse 2.0 data.
    \item The main advantage of this approach over traditional coverage analysis approaches is that it very easily scales to a large number of traffic scenarios.
    \item In other approaches (cite TNO Streetwise) it is necessary to manually define for each scenario type how it is defined. Here the only thing necessary is to define the actor graph construction rules as well as potentially the archetypes as graphs.
    \item 
    \item 
\end{itemize}
